---
title: "LICMA Evaluation"
output: github_document
---

# LICMA Evaluation Python 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
if(!require('pacman')) irnstall.packages("pacman")
pacman::p_load(dplyr, readr, stringr, ggplot2, here, viridis, forcats)
```

## Overview Misuses

```{r readMisuses, include = TRUE}
# TODO parametrize
misuses <- readr::read_csv2(here("evaluations", "evaluation-python-code", "python", "06_licma_analysis_results", "FINAL_licma-result-2020-08-06_152020507612.csv"))
misuses.distinct <- dplyr::distinct(misuses)

# Split Rule into RuleID and Lib
misuses <- misuses %>%
  tidyr::separate(Rule, c(NA, NA, "RuleID", "Lib"))
```

We got `r nrow(misuses)` misuses and `r nrow(misuses.distinct)` distinct misuses. 
We have no duplicated misuse: `r nrow(misuses) == nrow(misuses.distinct)`.

```{r ruleToLib, include=TRUE}
RuleID <- c("1", "2", "3", "4", "5")
ruleLib <- misuses %>%
  mutate(RuleID = factor(RuleID)) %>%
  mutate(Lib = factor(Lib)) %>%
  group_by(RuleID, Lib, .drop = F) %>%
  summarize(n = n()) 
ruleLib$RuleID <- factor(ruleLib$RuleID, levels = c ("5", "4", "3", "2", "1"))

ggplot(ruleLib, aes(x=factor(RuleID), y=n, fill=factor(Lib))) +
  geom_bar(aes(width=0.8), position="dodge", stat="identity")  +
  geom_text(aes(label = n), position = position_dodge(width = 0.85), size = 5, hjust = 0) + 
  coord_flip() + 
  scale_fill_viridis(discrete = TRUE, option = "D", drop = FALSE) +
  scale_x_discrete(labels=c("1" = expression("\u00A71"), "2" = expression("\u00A72"), "3" = expression("\u00A73"), "4" = expression("\u00A74"), "5" = expression("\u00A75"))) +
  ylab("Number of misuses") +
  ylim(0, 500) +
  facet_wrap(vars(Lib)) +
  theme(legend.position="none", axis.title.y = element_blank(), axis.title.x = element_text(size = 18, face = "italic"),text = element_text(size=18))
ggplot2::ggsave(here("evaluations", "evaluation-python-code", "python", "06_licma_analysis_results", "ruleLib.png"), width=200, height = 140, units = c("mm"), dpi = "print")
```

## Projects 

```{r projects}
# Get the projects of a misuse
misuses <- misuses %>%
  mutate(File = stringr::str_replace(File, "/media/ubuntu/DATA/repositories-python/", "")) %>%
  mutate(Project = stringr::str_extract(File, "(([^//]*))"))
  #mutate(Project = gsub("(//([^//]*))", "MATCH", File))

files <- misuses %>%
  group_by(File) %>%
  summarize(count = n()) %>%
  dplyr::arrange(desc(count))

projects <- misuses %>%
  group_by(Project) %>%
  summarize(count = n()) %>%
  dplyr::arrange(desc(count))

filesPerProject <- misuses %>%
  group_by(File, Project) %>%
  summarize(fpmisuses = n()) %>%
  group_by(Project) %>%
  mutate(filesProject = n()) %>%
  dplyr::arrange(desc(filesProject))
```

We have found misuses in `r nrow(files)` different files and in `r nrow(projects)` projects.

```{r filesPerProject}
ggplot(filesPerProject, aes("", filesProject)) + 
  geom_boxplot() + 
  coord_flip() +
  labs(y="# of files with misuses per project", x = "")
```

The distribution of the number of misuses per file and project (*fpmisuses*) and the number of files with a misuses per project (*filesProject*):
`r summary(filesPerProject)`

## Get Number of Projects and Files with Error 

```{r projectsFilesError}
# Read log file into R
log <- read.table(here("evaluations", "evaluation-python-code" , "python", "06_licma_analysis_results", "FINAL_licma2020-08-06_151938992667-log.txt"),
   header = FALSE, sep = "|")
log <- log %>%
  mutate(Status = str_trim(V2)) %>%
  mutate(Filepath = str_trim(V3))
readr::write_csv(log, "./log.csv")

# Get the error files (only parse problem due to "inconsistent" handling of |) 
error_files <- log %>%
  filter(Status == "ERROR") %>%
  filter(stringr::str_detect(Filepath, "parsing not possible: ")) %>%
  mutate(File = stringr::str_replace(Filepath, "parsing not possible: ", "")) %>%
  mutate(File = stringr::str_replace(File, "/media/ubuntu/DATA/repositories-python/", "")) %>%
  mutate(Project = stringr::str_extract(File, "(([^//]*))"))
projects_no_parse <- error_files %>%
  group_by(Project) %>%
  summarize(n = n()) %>%
  dplyr::arrange(desc(n))
View(error_files)

# Projects without successful parse and not included in misuses 
no_misuse_parse <- dplyr::anti_join(projects_no_parse, misuses, by="Project")

# Read helper file with maxrecursion cat FINAL_licma2020-08-06_151938992667-log.txt | rg "maximum recursion depth exceeded" > maxrecursion.txt
maxrecursion <- read.table(here("evaluations", "evaluation-python-code" , "python", "06_licma_analysis_results", "maxrecursion.txt"),
   header = FALSE, sep = "|")
maxrecursion <- maxrecursion %>%
  mutate(Filepath = str_trim(V6)) %>%
  mutate(File = stringr::str_replace(Filepath, "file: /media/ubuntu/DATA/repositories-python/", ""))  %>%
  mutate(Project = stringr::str_extract(File, "(([^//]*))"))
projects_recursion <- maxrecursion %>%
  group_by(Project) %>%
  summarize(n = n()) %>%
  dplyr::arrange(desc(n))

# Projects without max recursion and not included in missues
no_misuse_rec <- dplyr::anti_join(projects_recursion, misuses, by = "Project")

# Projects error
projects_error <- dplyr::bind_rows(projects_no_parse, projects_recursion) %>%
  group_by(Project) %>%
  summarize(n = n())
no_misuse <- dplyr::anti_join(projects_error, misuses, by = "Project")

# Check which of the projects run successful and did not result in a misuse
successfulanalysis <- log %>%
  filter(Status == "INFO") %>%
  filter(stringr::str_detect(Filepath, "processing: ")) %>%
  mutate(File = stringr::str_replace(Filepath, "processing: /media/ubuntu/DATA/repositories-python/", "")) %>%
  mutate(Project = stringr::str_extract(File, "(([^//]*))")) 
successfulanalysis_projects <- successfulanalysis %>%
  group_by(Project) %>%
  summarize(n = n()) %>%
  dplyr::arrange(desc(n))

# Check which projects cause and error and do not have a successful analysis run
kickedout <- dplyr::anti_join(projects_error, successfulanalysis_projects, by = "Project")
nrow(kickedout)
# At least one successful and one unsuccessful analysis run
both <- dplyr::semi_join(projects_error, successfulanalysis_projects, by = "Project")
#nrow(both)
#nrow(projects_error)
#nrow(successfulanalysis_projects)
```

In total, we have `r nrow(projects_no_parse) -1` projects which have files which do not parse.
From these projects, `r nrow(no_misuse_parse) -1` projects have no misuse in another file. 
In total, we have `r nrow(projects_recursion)` projects which have files which hits the maximum recursion.
From these projects, `r nrow(no_misuse_rec)` projects have no misuse in another file. 
Both sources of errors combined, `r nrow(projects_error)` projects cause an error while analyzing.
Of these projects, `r nrow(no_misuse)` projects have no misuse in another file. 
In total, we analyzed `r nrow(successfulanalysis_projects)` projects successfully. 
Of the projects causing an error, `r nrow(kickedout)` projects have no successful analysis of at least one class file. 

```{r code-dependencies}
dependencies <- misuses %>%
  filter(stringr::str_detect(File, "requirements_licma_analysis")) %>% 
  mutate(Loc = "Dep") 
repo <- misuses %>%
  filter(!stringr::str_detect(File, "requirements_licma_analysis")) %>% 
  mutate(Loc = "Repo")
misuses <- dplyr::bind_rows(dependencies, repo) 
```

```{r dependency-misuses-graph}
colnames(misuses)[colnames(misuses) == "Hit-Type"] <- "Hit"

misuses %>%
  group_by(Loc, Hit) %>%
  summarize(n = n()) %>%
  ggplot(aes(x=factor(Loc), y=n, fill=factor(Hit))) +
  geom_bar(stat="identity", position = "dodge")  +
#  geom_text(aes(label = n), size = 3, hjust= 1, vjust = 0.5, position = position_dodge(0.9)) +
  coord_flip() + 
  scale_fill_viridis(discrete = TRUE, option = "D", drop = FALSE) +
  ylab("Number of misuses") +
  xlab("Dependency or Application") 
```

```{r projectsOnlyDependencies}
projectsMisusesRepo <- misuses %>%
  filter(Loc == "Repo") %>%
  group_by(Project) %>%
  summarize(n = n()) %>%
  dplyr::arrange(desc(n))
nrow(projectsMisusesRepo)
summary(projectsMisusesRepo)
```


## Get the reasons of critical misuses

```{r criticalmisuses}
colnames(misuses)[colnames(misuses) == "Parameter-Value"] <- "ParameterValue"
critical <- misuses %>%
  filter(Hit == "critical")
description <- critical %>%
  group_by(Misuse) %>%
  summarize(n = n()) %>%
  dplyr::arrange(desc(n))
# hard coded int  
hardint <- critical %>%
  filter(stringr::str_detect(Misuse, "hard coded int"))
hardintprojects <- hardint %>%
  group_by(Project) %>%
  summarize(n = n()) %>%
  dplyr::arrange(desc(n))
hardintvalue <- hardint %>%
  group_by(ParameterValue) %>%
  summarize(n = n()) %>%
  dplyr::arrange(desc(n))

# hard coded byte
hardbyte <- critical %>%
  filter(stringr::str_detect(Misuse, "hard coded byte"))
hardbyteprojects <- hardbyte %>%
  group_by(Project) %>% 
  summarize(n = n())
# ECB
ecb <- critical %>%
  filter(ParameterValue == "MODE_ECB")
View(ecb)
hardcodedattribute <- description %>% filter(stringr::str_detect(Misuse, "hard coded attribute"))
ecbprojects <- ecb %>%
  group_by(Project) %>%
  summarize(n = n()) %>%
  dplyr::arrange(desc(n))
rule1 <- critical %>%
  filter(RuleID == "1")

## Rule 2: Do not use a non-random initiliazationvector (IV) for ciphertext block chaining(CBC) encryption
rule2 <- critical %>%
  filter(RuleID == "2")
rule2projects <- rule2 %>%
  group_by(Project) %>%
  summarize(n =n ())

## Rule 3: Do not use constant encryption keys.
rule3 <- critical %>%
  filter(RuleID == "3")
rule3projects <- rule3 %>%
  group_by(Project) %>%
  summarize(n = n())
View(critical)

# Rule 4: Do not use constant salts for password-based encryption (PBE).
rule4 <- critical %>%
  filter(RuleID == "4")
rule4projects <- rule4 %>% 
  group_by(Project) %>%
  summarize(n = n())
print(rule4[[17,1]])

# Rule 5: Do not use fewer than 1,000 iterationsfor PBE.
rule5 <- critical %>%
  filter(RuleID == "5")
rule5projects <- rule5 %>%
  group_by(Project) %>%
  summarize(n = n())

# Number of critical projects
criticalprojects <- critical %>%
  group_by(Project) %>%
  summarize(n = n())
```

Of the `r nrow(critical)` critical misuses, we identified:

- a misuse due to ECB mode for `r nrow(ecb)` which covers all hard coded attribute misuses: `r nrow(ecb) == hardcodedattribute$n`. ECB was used as encryption mode within `r nrow(ecbprojects)` projects. All misuses due to ECB are misuse due to rule 1 (should be): `r nrow(rule1) == nrow(ecb)`.
- a hard coded byte for AES.new and improper init (Rule 2): `r nrow(rule2)` within `r nrow(rule2projects)` projects. 
  - Example of a static IV: https://github.com/SecureAuthCorp/impacket/blob/master/impacket/krb5/crypto.py#L435
- a constant encryption key (Rule 3): `r nrow(rule3)` misuses within `r nrow(rule3projects)` projects 
  - Example of a static key: https://github.com/secdev/scapy/blob/master/scapy/layers/tls/crypto/cipher_stream.py#L57 (parameter) within line https://github.com/secdev/scapy/blob/master/scapy/layers/tls/crypto/cipher_stream.py#L62
  - For two projects, these are duplicates due to scapy (repo & dependency) 
- a constant salt for PBE (Rule 4): `r nrow(rule4)` misuses within `r nrow(rule4projects)` projects
  - Example of a constant salt: https://github.com/jrnl-org/jrnl/blob/develop/jrnl/EncryptedJournal.py#L31
  - Another example like in our business study that the value is empty if the loop isn't entered: https://github.com/cloudera/hue/blob/master/desktop/core/ext-py/pycryptodomex-3.9.7/lib/Cryptodome/Protocol/KDF.py#L405 
- Fewer than 1000 iterations (Rule 5): `r nrow(rule5)` misuses within `r nrow(rule5projects)` projects
  - a hard coded int PDKDF2 for `r nrow(hardint)` within `r nrow(hardintprojects)` different projects. All (`r nrow(hardint) == hardintvalue$n`) misuses due to a hard coded integer value have the value 1 (iteration count should be higher than 1000). 
    - Example that iteration count is one: https://github.com/cloudera/hue/blob/8aa24a89648ab7c079cbce7369481fefbc05efc7/desktop/core/ext-py/pycryptodomex-3.9.7/lib/Cryptodome/Protocol/KDF.py#L385
    - Example that iteration count is one: https://github.com/cloudera/hue/blob/8aa24a89648ab7c079cbce7369481fefbc05efc7/desktop/core/ext-py/pycryptodomex-3.9.7/lib/Cryptodome/Protocol/KDF.py#L406
- `r nrow(criticalprojects)` distinct projects are affected by critical misuses. 

```{r criticalmisusesrules}
critical %>%
  group_by(RuleID) %>%
  summarize(n = n()) %>%
  ggplot(aes(x=factor(RuleID), y=n)) +
  geom_bar(position="dodge", stat="identity")  +
  geom_text(aes(label = n), position = position_dodge(width = 0.85), size = 3, hjust = - 0.5) + 
  coord_flip() + 
  scale_fill_viridis(discrete = TRUE, option = "D", drop = FALSE) +
  ylab("Number of misuses") +
  xlab("Rule") +
  theme(legend.position="none")
```

## Further investigations to understand the data 


### Dependencies within the application code via the *ext-py* folder

```{r extpy}
extpy <- repo %>%
  filter(stringr::str_detect(File, "ext-py"))
extpyproj <- extpy %>%
  group_by(Project) %>%
  summarize(n = n())
```

In total, we have `r nrow(extpy)` (`r nrow(extpy) / nrow(repo) * 100`) misuses with *ext-py* within the path name. This affects `r nrow(extpyproj)` different projects. 

## Graphs for the Paper

```{r TopReposMisuses}
misusesgrouped <- misuses %>%
    group_by(Project, Loc) %>%
    summarize(n = n()) %>%
    group_by(Project) %>%
    mutate(projmisuses = sum(n)) %>%
    filter(projmisuses > 30) %>%
    ungroup() %>%
    mutate(Project= fct_reorder(Project, projmisuses))
ggplot(misusesgrouped, aes(x = Project, y = n, fill = Loc)) +
  geom_bar(aes(width = 0.7), stat = "identity") +
  #Add the number of misuses correctly within each bar.
  geom_text(aes(label = n, group = Loc), position = position_stack(vjust = 0.9), size = 5) +
  coord_flip() +
  ylab("Number of missues per GitHub project") +
  labs(fill = "Location") +
  theme(axis.title.y = element_blank(),axis.title.x = element_text(size = 18, face = "italic"),text = element_text(size = 18)) +
  theme(legend.position = c(1, 0), legend.justification = c(1, 0)) +
  scale_x_discrete(labels = function(x){sub("__", "\n/", x)}) +
  scale_fill_viridis(discrete = TRUE, option = "D", begin = 0.7, end = 0.9,  drop = FALSE, labels = c("Dependency", "Application"))
ggplot2::ggsave(here("evaluations", "evaluation-python-code", "python", "06_licma_analysis_results", "toprepos.png"), width=200, height = 140, units = c("mm"), dpi = "print")
``` 

```{r TopDepsMisuses}
View(misuses)
```