---
title: "LICMA Meta-analysis"
output: github_document
---

# LICMA Meta-analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
if(!require('pacman')) irnstall.packages("pacman")
pacman::p_load(dplyr, readr, stringr, ggplot2, here, viridis)
```

## Misuses per Rule for LICMA

```{r readMisuses, include = TRUE}
# TODO parametrize
misuses <- readr::read_csv2(here("evaluations", "evaluation-python-code", "python", "06_licma_analysis_results", "FINAL_licma-result-2020-08-06_152020507612.csv"))
# Add the information about the project into the data frame
misuses <- misuses  %>%
  mutate(File = stringr::str_replace(File, "/media/ubuntu/DATA/repositories-python/", "")) %>%
  mutate(Project = stringr::str_extract(File, "(([^//]*))"))
colnames(misuses)[colnames(misuses) == "Hit-Type"] <- "Hit"

# Split Rule into RuleID and Lib
misuses <- misuses %>%
  tidyr::separate(Rule, c(NA, NA, "RuleID", "Lib"))

licmacritical <- misuses %>%
  filter(Hit == "critical") %>%
  group_by(RuleID) %>%
  summarize(n = n()) %>%
  mutate(perc = n / 85 * 100)

licmaapsscritical <- misuses %>%
  filter(Hit == "critical") %>%
  group_by(RuleID, Project) %>%
  summarize(helper = n()) %>%
  group_by(RuleID) %>%
  summarize(n = n()) %>%
  mutate(perc = n / 155 * 100)
```



`r knitr::kable(licmacritical, caption = "Distribution of Misuses to Rules for Critical Misuses") `
`r knitr::kable(licmaapsscritical, caption = "Distribution of Projects with at least one Misuse of one Rule for Critical Misuses") `

## Misuses per Rule for CryptoLint

The Evaluation by Egele et al. focuses on the number of apps which violates one rule rather than the total number of observed misuses per rule. 

```{r misusescryptolint, include = TRUE}
RuleID <- c("1", "2", "3", "4", "5", "No")

n <- c(7656, 1932, 3644, 1574, 1636, 1421)
egele <- data.frame(RuleID, n)
numberAnalyzed <- 11748
egele <- egele %>%
  mutate(perc = n / numberAnalyzed * 100)
```

`r knitr::kable(egele, caption = "Distribution of Projects with at least one Misuse of the Respective Rule")`

## Misuses per Rule for CryptoRex

The evaluation by Zheng et al. may missed to discuss how many of the firmware images do not use crypto. 
While their describe filtering for crypto usages, their text read as that the **521** firmware images are before the filter step.
Thus, the percentages are for misuses may be upon the unfiltered data set. 

```{r misusescryptorex, include = TRUE}
# Numbers from Table 4 Zhang et al. CryptoRex 2019. 
n <- c(107, 24, 59, 56, 23, 395) 
zhang <- data.frame(RuleID, n)
numberAnalyzed <- 521
zhang <- zhang %>%
  mutate(perc = n / numberAnalyzed * 100)
```

`r knitr::kable(zhang, caption = "Distribution of Firmware images with at least one misuse of the respective rule")`

## Graphs

```{r metaanalysis, include = TRUE}
# Add no row
n <- c(5, 6, 2, 14, 13, 137) # 18 distinct projects are affected by critical misuse.
numberAnalyzed <- 155
licma <- data.frame(RuleID, n)
licma <- licma %>% 
  mutate(perc = n / numberAnalyzed * 100)
licma$study = "LICMA_critical"
#licmaapsscritical$study = "LICMA_critical"

egele$study = "CryptoLint"
zhang$study = "CryptoRex"
#meta <- dplyr::bind_rows(licmaapsscritical, egele, zhang)  %>%
meta <- dplyr::bind_rows(licma, egele, zhang)  %>%
  mutate(RuleID = factor(RuleID, levels=c("No", "5", "4", "3", "2", "1")))

ggplot(meta, aes(x=factor(RuleID), y=perc, fill = study)) +
  geom_bar(position="dodge", stat="identity")  +
  geom_text(aes(label = format(round(perc, 2))),  position=position_dodge(width=0.9), vjust=0.5, hjust=-0.15, size = 5) + 
#  geom_text(data = meta %>% filter(perc > 65), aes(label = format(round(perc, 2))),  position=position_dodge(width=0.9), vjust=0.25, hjust=4) + 
  scale_x_discrete(labels=c("1" = expression("\u00A71"), "2" = expression("\u00A72"), "3" = expression("\u00A73"), "4" = expression("\u00A74"), "5" = expression("\u00A75"), "No" = "No")) +
  scale_fill_viridis(discrete = TRUE, option = "D", begin = 0.5, end = 1, drop = FALSE , labels = c("Java: CryptoLint", "C: CryptoRex", "Python: LICMA")) +
  ylab("Percentage of applications with a misuse") +
  labs(fill = "Study") +
  xlab("Rule") +
  ylim(0, 94) + 
  coord_flip() + 
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 18, face = "italic"),
    text=element_text(size=18),
    legend.position = c(1,0.5), legend.justification = c(1,0.5)
   )  
ggplot2::ggsave(here("evaluations", "evaluation-python-code", "python", "06_licma_analysis_results","./meta.png"), width=200, height = 100, units = c("mm"), dpi = "print")
```

